THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-06-28 DishReflectometry/Paper1_v2.tex

\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$, corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the delay spectrum of the visibility measured by an interferometer. The sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12]. The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum, $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.

@@

\subsection{Feed effect: zero delay correction}
%At first, the frequency domain measurement of s11 is Fourier-transformed to compute the response of the system in the delay domain.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{plots/VNA_RL.png}
\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable. This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
\label{fig:window}
\end{figure}

>>>>

\indent Since both $k_{\perp}$ and $k_{\parallel}$ are functions of the delay $\tau$, corresponding to the given baseline length, the redshifted 21 cm power spectrum could be estimated from the delay spectrum of the visibility measured by an interferometer. The sky delay spectrum from any direction $\thhat$ is convolved with the delay spectrum of the instrument and would be located at the delay $\tau = {\vec b \cdot \thhat \over c}$ %defined this differently earlier
 in the delay domain. The maximum geometric delay possible for a given baseline would be $\tau_{g} ={ b \over c }$ for the direction of $\thhat = 0$, when the phase centre is halfway in between the two antennas. %The phase center is elsewhere defined as being at the center of one of the antennas.
 Hence, the sky contribution from any direction would be confined within $-\tau_{g}<\tau<\tau_{g}$. Due to the chromaticity of the sky signal as well as the instrument response, the delay spectrum of the sky spills over into delays with $\tau> \tau_{g}$, with a decaying amplitude [Ref to the Figure Parsons12]. The foreground, $P_{fg}(\tau)$, which is spectrally smooth, and the 21~cm power spectrum, $P_{21}(\tau)$, which contains spectral signatures, contribute to the sky delay spectrum $P_{sky}(\tau)$.Therefore, in the spill over region $(\tau>\tau_{g})$, the relative strength of the smooth spectrum foreground, with respect to the delay spectrum of the $I_{21}$, reduces and the 21cm delay spectrum could be detectable.

@@

@@

%\begin{figure}
%\centering
%\includegraphics[width=\linewidth]{plots/VNA_RL.png}
%\caption{Magnitude and phase of the combined effects of the return loss at the VNA input alone with the cable resistive loss as computed from the return loss measurement of the open load at the feed input of the cable. This is consistent with the specifications of the RF connectors which is commonly used at low frequencies }
%\label{fig:window}
%\end{figure}
